\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-27 paper.tex
explained more about features

@@

\nocite{harvey2002} % don't remove this

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of the ARuko in order to conduct some final testing. We met up
with Atticus, the IQP group, and our intern Hikaru and installed the beta
version of ARuko on each of their phones. With little instruction about how the
app works we had each of them try going through Kinkaku-ji while listening to
the tour and using the app's features. Each member of our team also installed
the beta version so we could fuzz test it.

This was our first time trying the AR image recognition on the actual signs at
Kinkaku-ji, rather than photographs of the signs, and it worked quite well.
Vuforia was able to recognize all of the signs, even in different lighting than
when the reference images were taken. For image targets that were small, far
away, or obscured by shadows image recognition was slower, but Vuforia was
always able to recognize them eventually. We discovered that the targets that
worked best were large, had a lot of high-contrast text, and were uniformly lit.

While testing we discovered some issues with the design of the tour. One region
was completely misplaced, so the audio played at the wrong time while walking
through the area. Several other regions were too big, so the audio started
playing long before the user was actually near the feature it was discussing.
Finally, one of the image targets had the wrong text in its information pop-up.
These were all easy bugs to fix, but if we might not have noticed them if we
had not tested the app on site.

>>>>

\subsubsection{Translation Feature}
\label{sec:translationFeature}

Despite Kinkaku-ji being an incredibly popular tourist destination that draws
crowds from all over the world, the majority of the signage is purely
Japanese. While AR translation apps exist, the experience can be frustrating,
and produce poor results. Google's text recognition and machine-learning
powered translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant''
mode. In ``instant'' mode, the app attempts to translate text as quickly as
possible and superimpose the translated text onto the real world using the
camera. In ``scan'' mode, the user takes a photo. Then, the user is prompted
to highlight where text appears in the photo. After the translation is
complete, the translated text appears in a separate UI element instead
superimposed onto the photo. In most cases, it is more convenient and
readable to have the translation appear in a separate scrollable textbox.
This motivated the current design of the ``info buttons'' in ARuko. Instead
of placing text directly onto signage, we place a blue button with an `i' in
the center. By tapping on this button, a separate UI element will appear
containing the translated text. Since this button is cast into the world
using the AR camera, the button is intuitively placed directly onto the
content in the real world.

\subsubsection{Virtual Souvenir Feature}
\label{sec:virtualSouveneir}

When you buy a ticket to enter Kinkaku-ji, you receive a long sheet of
printed paper with calligraphy. The tickets are large and visually appealing;
they are souvenirs unto themselves that one might feel inclined to keep
around. Over the course of our three month stay we visited Kinkaku-ji
multiple times. For each visit, we received identical tickets. Seemingly, the
design on the tickets do not change on a regular basis, if at all.

Because the tickets are unlikely to change, this enables us to provide the
user with a ``virtual souvenir'' using the AR camera. This is the only AR
feature that is not tied directly to an image target that can only be
accessed at Kinkaku-ji. While the image gallery and segments of the audio
tour can be accessed at any time using the ``Chapter Select'' menu, most of 
the AR features can only be experienced during the walking tour, pointing the 
camera at objects physically located at the site. Augmenting the ticket
with 3D content allows visitors to take something home, giving them a reason
to launch the app later.

We found a free untextured model of the Golden Pavilion to use for this
feature. Using Unity's built-in capability to design materials, we created
a shiny golden material and applied it to the model.

Originally, the AR model of the Golden Pavilion was flush against the plane
of the ticket, sitting on the paper as if it were ground. Atticus suggested
that we re-orient the model such that the ticket served as a back plane. This
would allow users to hold the ticket vertically, and view the Golden Pavilion
floating in front of the ticket. This would allow users to place their hands
under the base of the Golden Pavilion model as if they were holding it.
Vuforia's image tracking is flexible enough such that the image target can be
partially obscured.

@@

% TODO remove this
\nocite{harvey2002} % don't remove this

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of the ARuko in order to conduct some final testing. We met
up with Atticus, the IQP group, and our friend Hikaru and installed the beta
version of ARuko on each of their phones. With little instruction about how
the app works we had each of them try going through Kinkaku-ji while
listening to the tour and using the app's features. Each member of our team
also installed the beta version so we could fuzz test it.

This was our first time trying the AR image recognition on the actual signs
at Kinkaku-ji, rather than photographs of the signs, and it worked quite
well. Vuforia was able to recognize almost all of the signs, even in
different lighting than when the reference images were taken. For image
targets that were small, far away, or obscured by shadows image recognition
was slower, but Vuforia was always able to recognize them eventually. We
discovered that the targets that worked best were large, had a lot of
high-contrast text, and were uniformly lit.

While testing we discovered some issues with the design of the tour. One
region was completely misplaced, so the audio played at the wrong time while
walking through the area. Several other regions were too big, so the audio
started playing long before the user was actually near the feature it was
discussing. Using the Editour web-app, we were able to correct quickly these
issues with the tour design once we returned to Atticus' office.

Additionally, one of the image targets had the wrong text in its information
pop-up. These were all easy bugs to fix, but if we might not have noticed
them if we had not tested the app on site.

Similarly, we noticed that we were only able to augment a maximum of two
image targets at a time. In almost all cases, only two translatable signs
were in view at once. The only scenario in which there were more than two
image targets in view at a given time was with the four framed photos of the
interior, arranged in a two by two grid. When standing at a distance from the
grid, only two images would be augmented with the blue information button. By
default, Vuforia limits the amount of image targets that the engine should
accept simultaneously. In the Vuforia engine settings, we changed this limit
to accommodate for four simultaneous images
